Reinforcement \change{L}earning for \change{O}ptions\\on \change{T}arget \change{V}olatility \change{F}unds\thanks{Supported by ISCRA from Cineca, \email{iscra@cineca.it}.}

### 2023-02-25 tex/m2ef/daluiso_nastasi_pallavicini_polo_rl_for_options_on_tvf.tex
add minibatch definition

\begin{abstract}
We deal with \remove{the funding costs} \change{a stochastic optimal control problem} rising from hedging the risky securities underlying a target volatility strategy (TVS), a portfolio \remove{of risky assets and a risk-free one dynamically rebalanced in order to keep the} \change{whose asset-allocation is adjusted to mantain the} realized volatility of the portfolio on a certain level. \change{We consider the point of view of a derivative writer selling an option contract as protection to a portfolio manager on the capital invested in a TVS.} The uncertainty in the TVS risky portfolio composition along with the difference in hedging costs \change{of its} \remove{for each} component requires to \remove{solve a control problem to evaluate the option} \change{adjust the protection} price\remove{s} \change{to include these costs in the worst-case scenario for the seller}. We derive an analytical solution of the problem in the Black and Scholes (BS) scenario. Then we use Reinforcement Learning (RL) techniques to determine the fund composition leading to the \remove{most conservative price} \change{optimal policy} under the local volatility (LV) model, for which an {\it a priori} solution is not available. We show how the performances of the RL agents are compatible with those obtained by applying path-wise the BS analytical strategy to the TVS dynamics, which therefore appears competitive also in the LV scenario.

@@

In this work we tackle the non-trivial case of a local volatility (LV) model for the $S_t$-dynamics, such that $\nu_t = \nu(t,S_t)$. We have chosen the LV model since it is well known in financial literature and among practitioners \change{\cite{Gatheral2006}}.

@@

Because of that, we change the learning strategy by adopting a more sophisticated one: the PPO algorithm. The big advantage of PPO is that, in addition to the policy, a guess of the value function in Equation~\eqref{eq:HJB_general} is also computed by a parameterization through an FFNN. As for the direct policy approach, we use the BS environment to fine-tune the PPO hyper-parameters. Again we experienced that deeper FFNNs outperform shallow ones and tanh is the most preferable. We report for completeness the values of the other PPO hyper-parameters, for the description of which we refer to \cite{Schulman2017}: learning rate $3\times 10^{-4}$, $\lambda=0.95$, $\epsilon=0.2$, $c_1=0.7$, $c_2=0$ and mini-batch size of 2048 episodes.

>>>>

\begin{abstract}
We deal with \remove{the funding costs} \change{a stochastic optimal control problem} rising from hedging the risky securities underlying a target volatility strategy (TVS), a portfolio \remove{of risky assets and a risk-free one dynamically rebalanced in order to keep the} \change{whose asset-allocation is adjusted to maintain the} realized volatility of the portfolio on a certain level. \change{We consider the point of view of a derivative writer selling an option contract as protection to a portfolio manager on the capital invested in a TVS.} The uncertainty in the TVS risky portfolio composition along with the difference in hedging costs \change{of its} \remove{for each} component requires to \remove{solve a control problem to evaluate the option} \change{adjust the protection} price\remove{s} \change{to include these costs in the worst-case scenario for the seller}. We derive an analytical solution of the problem in the Black and Scholes (BS) scenario. Then we use Reinforcement Learning (RL) techniques to determine the fund composition leading to the \remove{most conservative price} \change{optimal policy} under the local volatility (LV) model, for which an {\it a priori} solution is not available. We show how the performances of the RL agents are compatible with those obtained by applying path-wise the BS analytical strategy to the TVS dynamics, which therefore appears competitive also in the LV scenario.

@@

In this work we tackle the non-trivial case of a local volatility \remove{(LV)} model for the $S_t$-dynamics, such that $\nu_t = \nu(t,S_t)$. We have chosen the LV model since it is well known in financial literature and among practitioners \change{\cite{Gatheral2006}}.

@@

Because of that, we change the learning strategy by adopting a more sophisticated one: the PPO algorithm. The big advantage of PPO is that, in addition to the policy, a guess of the value function in Equation~\eqref{eq:HJB_general} is also computed by a parameterization through an FFNN. As for the direct policy approach, we use the BS environment to fine-tune the PPO hyper-parameters. Again we experienced that deeper FFNNs outperform shallow ones and tanh is the most preferable. We report for completeness the values of the other PPO hyper-parameters, for the description of which we refer to \cite{Schulman2017}: learning rate $3\times 10^{-4}$, $\lambda=0.95$, $\epsilon=0.2$, $c_1=0.7$, $c_2=0$ and mini-batch\footnote{\change{A minibatch is a subset of a larger dataset, which is used to train a machine learning model. The model updates its parameters based on the error calculated from the predictions it makes on each minibatch. This allows for more efficient memory use, faster convergence of the model, and better generalization to new data.}} size of 2048 episodes.
